Matching Bullets

### 2015-11-24 imaging-paper.Rnw
Include float to fix some errors in building
Describe rifling procedure, clean up footnotes

\usepackage[USenglish]{babel}
\usepackage[protrusion=true,expansion=true]{microtype} % Better typography
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage[svgnames]{xcolor} % Enabling colors by their 'svgnames'
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{fix-cm}	 % Custom font sizes - used for the initial letter in the document

@@

\usepackage{color}
\newcommand{\hh}[1]{{\color{magenta} #1}}

@@

Rough outline:
\begin{enumerate}
\item Description of the problem: Standard operating practice, 2009 NAS report
\item Description of the Results
\item Walkthrough of the process
\item \hh{XXX Alternative approaches: IBIS database and the NRC report against it\footnote{Fox report on the NRC report \url{http://www.foxnews.com/story/2008/03/05/nationwide-firearms-database-shot-down-by-government-sponsored-study.html}.
NRC report: \url{http://www.nap.edu/catalog/12162/ballistic-imaging}} }
\end{enumerate}

@@

\hh{XXX here's a paragraph missing: rifling in the barrel is creating striation marks on the bullet during the firing process (and grooves). These marks are claimed to be unique to the barrel - we need to find a citation for that from the SOP manual. Roger Thompson's writeup on firearm identification cites AFTE 1992 procedures.\footnote{\url{https://www.ncjrs.gov/app/publications/Abstract.aspx?id=254151}}, \footnote{AFTE 1992 theory of identification \url{http://projects.nfstc.org/firearms/module09/fir_m09_t05_05.htm}} includes the following statements, both on page 34: `The theory of identification as it pertains to the comparison of toolmarks enables opinions of common origin to be made when the \emph{unique surface contours} of two toolmarks are in ``sufficient agreement".' (my highlighting) and `Significance is determined by the comparative examination of two or more sets of surface contour patterns comprised of individual peaks, ridges and furrows.'}

>>>>

\usepackage[USenglish]{babel}
\usepackage[protrusion=true,expansion=true]{microtype} % Better typography
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage[svgnames]{xcolor} % Enabling colors by their 'svgnames'
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{fix-cm}	 % Custom font sizes - used for the initial letter in the document
\usepackage{float}

@@

\usepackage{color}
\newcommand{\hh}[1]{{\color{magenta} #1}}
\newcommand{\eh}[1]{{\color{blue} #1}}

@@

Rough outline:
\begin{enumerate}
\item Description of the problem: Standard operating practice, 2009 NAS report
\item Description of the Results
\item Walkthrough of the process
\item \hh{XXX Alternative approaches: IBIS database and the NRC report against it\footnote{Fox report on the NRC report \url{http://www.foxnews.com/story/2008/03/05/nationwide-firearms-
database-shot-down-by-government-sponsored-study.html}.
NRC report: \url{http://www.nap.edu/catalog/12162/ballistic-imaging}} }
\end{enumerate}

@@

Rifling in the barrel creates striation marks on the bullet during the firing process (and grooves). These marks are claimed to be unique to the barrel, as described in a 1992 AFTE article. ``The theory of identification as it pertains to the comparison of toolmarks enables opinions of common origin to be made when the \emph{unique surface contours} of two toolmarks are in sufficient agreement" The article goes on to state that ``Significance is determined by the comparative examination of two or more sets of surface contour patterns comprised of individual peaks, ridges and furrows." \footnote{\url{https://www.ncjrs.gov/app/publications/Abstract.aspx?id=254151}}, \footnote{AFTE 1992 theory of identification \url{http://projects.nfstc.org/firearms/module09/fir_m09_t05_05.htm}}
